\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2022-11-04 PaperPreliminary.tex
Refs for paper + progress 11

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

% \documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out
%                                                           % if you need a4paper
\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4
                                                         % paper

\IEEEoverridecommandlockouts                              % This command is only
                                                          % needed if you want to
                                                          % use the \thanks command
\overrideIEEEmargins
% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

Automation has historically played a crucial role in the logistics industry. Our current way of living depends on autonomous systems for global transportation and warehousing. The growing labor shortage and increasing demand for online retail motivate further developments in the logistics sector [A Dekhne].

A logistical aspect where machines sometimes struggle to compete with humans is object manipulation. Practical examples include order picking or depalletizing. While robots are strong and consistent when manipulating objects, humans are flexible and swift. Robots are held back from faster performance because they must often slow down prior to making contact; establishing contact at a high velocity -- an event referred to as an impact -- could cause damage to the robot or its environment. On the contrary, humans intrinsically exploit impacts in the form of grabbing, bouncing and hitting.

The field of impact-aware control aims to better equip robots for making contact at high velocities. These impacts are paired with large contact forces that could damage the system. Previous work describes model predictive control using the maximum allowable impact velocity that complies with safety constraints such as limits for the contact force []. This was combined with a compliant cover for the robot that reduces contact forces at impact, facilitating higher feasible impact velocities. Rather than using a soft cover, compliancy may also be achieved by designing a robot with low inertia and high backdrivability as was done in [].

In addition to the large contact forces, the velocity jump at the time of impact is also a subject of interest. Time misalignments between velocity jumps in the reference and in the actual system cause the velocity tracking error to peak[], as is shown in Figure xxx. This error peak results in undesired control effort and should therefore be avoided. In [], the robot's velocities are projected into an impact-invariant subspace based on the expected point of impact. As a result, impact-driven peaks in the velocity tracking error are reduced significantly. It is not always possible to describe a point of impact, however. Often times, impacts occur between surfaces rather than just points. Furthermore, corners of the surface may impact at diverging intervals in uncertain order during what is called near-simultaneous impacts, shown in Figure xxx.

The impact-aware control scheme called Reference Spreading also addresses error peaking caused by misaligned impacts. It operates on the basis of a tracking error that switches once an impact is detected. This concept is best explained at the hand of Figure xxx. The reference is split at the nominal impact time into an ante- and post impact reference. These references are then extended. Initially, the tracking error is based on the extended ante-impact reference, but this is switched to the post-impact reference once an impact is detected. Evidently, this can reduce the error peaking.

Reference spreading can also handle simultaneous impacts. (explanation)

By addressing the peaking error, reference spreading facilitates faster object manipulation, making it interesting to industry if its effectivity can be proven in practice. Reference spreading for object manipulation has already been validated in simulations []. Experimental validations have been limited to interaction with a fixed environment, however []. The goal of this work is therefore to \textbf{provide a real-world implementation of reference spreading for practical object manipulation tasks.} To translate the results from simulation to this reality, the following contributions are made:

\textbf{1. Motion planning for impacts without object models}: Generating a reference with velocity jumps that is coherent with the system’s dynamics is challenging. 
One approach maps the ante-impact velocity to the post-impact velocity based on conservation of momentum []. This approach requires a model of the environment, which is feasible in simulations with simplified dynamics, but challenging in reality.
Impact-driven velocity jumps could instead be inferred experimentally. In previous studies[], the control gains are reduced to zero upon detection of the impact while inferring an impact map, so that the velocity jump would not results in excessive motor torques.
A different model-free motion planning strategy is proposed, which not only produces velocity jumps that are coherent with the system dynamics, but also leverages human intuition to generate fluid motions before and after the impact. (This strategy introduces a human in the loop by means of teleoperation; the operator performs a demonstration, after which a reference can be extracted. During the demonstration, the control gains are relatively low. This mitigates the torque jumps at the time of impact, meaning that the controller does not need to be turned off. The teleoperator instinctively accounts for the low control gains and can perform precise motion tasks despite poor tracking of the controller.)

\textbf{2. }

\begin{itemize}
\item hoi
\end{itemize}

words: warehouse, material handling, packaging, transport
\section{PROCEDURE FOR PAPER SUBMISSION}

@@

\section{MATH}

@@

\section{USING THE TEMPLATE}

@@

\section{CONCLUSIONS}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{APPENDIX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, ``Synthetic structure of industrial plastics (Book style with paper title and editor),''  in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15--64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123--135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, ``An approach to graphs of linear forms (Unpublished work style),'' unpublished.
\bibitem{c5} E. H. Miller, ``A note on reflector arrays (Periodical styleÑAccepted for publication),'' IEEE Trans. Antennas Propagat., to be publised.
\bibitem{c6} J. Wang, ``Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),'' IEEE J. Quantum Electron., submitted for publication.
\bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
\bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),'' IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740--741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
\bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
\bibitem{c10} J. U. Duncombe, ``Infrared navigationÑPart I: An assessment of feasibility (Periodical style),'' IEEE Trans. Electron Devices, vol. ED-11, pp. 34--39, Jan. 1959.
\bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ``A clustering technique for digital communications channel equalization using radial basis function networks,'' IEEE Trans. Neural Networks, vol. 4, pp. 570--578, July 1993.
\bibitem{c12} R. W. Lucky, ``Automatic equalization for digital communication,'' Bell Syst. Tech. J., vol. 44, no. 4, pp. 547--588, Apr. 1965.
\bibitem{c13} S. P. Bingulac, ``On the compatibility of adaptive controllers (Published Conference Proceedings style),'' in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8--16.
\bibitem{c14} G. R. Faulhaber, ``Design of service systems with priority reservation,'' in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3--8.
\bibitem{c15} W. D. Doyle, ``Magnetization reversal in films with biaxial anisotropy,'' in 1987 Proc. INTERMAG Conf., pp. 2.2-1--2.2-6.
\bibitem{c16} G. W. Juette and L. E. Zeffanella, ``Radio noise currents n short sections on bundle conductors (Presented Conference Paper style),'' presented at the IEEE Summer power Meeting, Dallas, TX, June 22--27, 1990, Paper 90 SM 690-0 PWRS.
\bibitem{c17} J. G. Kreifeldt, ``An analysis of surface-detected EMG as an amplitude-modulated noise,'' presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
\bibitem{c18} J. Williams, ``Narrow-band analyzer (Thesis or Dissertation style),'' Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
\bibitem{c19} N. Kawasaki, ``Parametric study of thermal and chemical nonequilibrium nozzle flow,'' M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
\bibitem{c20} J. P. Wilkinson, ``Nonlinear resonant circuit devices (Patent style),'' U.S. Patent 3 624 12, July 16, 1990.

\end{thebibliography}

>>>>

% Setup
    \documentclass[a4paper, 10pt, conference]{ieeeconf}
    \IEEEoverridecommandlockouts                              % This command is only
                                                              % needed if you want to
                                                              % use the \thanks command
    \overrideIEEEmargins
    % See the \addtolength command later in the file to balance the column lengths
    % on the last page of the document

@@

    \input{bibconfig.tex}

@@

% Abstract
    \begin{abstract}

@@

% Introduction
    \section{INTRODUCTION}

    Automation has historically played a crucial role in the logistics industry. Our current way of living depends on autonomous systems for global transportation and warehousing. The growing labor shortage and increasing demand for online retail motivate further developments in the logistics sector~\cite{dekhneAutomationLogisticsBig2019}.

    A logistical aspect where machines sometimes struggle to compete with humans is object manipulation. Practical examples of this include order picking or depalletizing. While robots are strong and consistent when manipulating objects, humans are versatile and swift. Robots are held back from faster performance because they must often slow down prior to making contact; establishing contact at a high velocity -- an event referred to as an impact -- could cause damage to the robot or its environment. On the contrary, humans intrinsically exploit impacts in the form of grabbing, bouncing and hitting.

    The field of impact-aware control aims to better equip robots for making contact at high velocities. These impacts are paired with large contact forces that could damage the system. Previous work describes model predictive control using the maximum allowable impact velocity that complies with safety constraints such as limits for the contact force~\cite{dehioRobotSafeImpactsSoft2021, dehioDualArmBoxGrabbing2022}. This was combined with a compliant cover for the robot that reduces contact forces at impact, facilitating higher feasible impact velocities. Rather than using a soft cover, compliancy may also be achieved by designing a robot with low inertia and high backdrivability as was done in \cite{songDevelopmentLowInertiaHighStiffness2018}.

    In addition to the large contact forces, the velocity jump at the time of impact is also a subject of interest. Time misalignments between velocity jumps in the reference and in the actual system cause the velocity tracking error to peak\cite{biemondTrackingControlMechanical2012}, as is shown in Figure xxx. This error peak results in undesired control effort and should therefore be avoided. In \cite{yangImpactInvariantControl2021}, the robot's velocities are projected into an impact-invariant subspace based on the expected point of impact. As a result, impact-driven peaks in the velocity tracking error are reduced significantly. It is not always possible to describe a point of impact, however. Often times, impacts occur between surfaces rather than just points. Furthermore, corners of the surface may impact at diverging intervals in uncertain order during what is called near-simultaneous impacts, shown in Figure xxx.

    The impact-aware control scheme called Reference Spreading \cite{sacconSensitivityAnalysisHybrid2014} also addresses error peaking caused by misaligned impacts. It operates on the basis of a tracking error that switches once an impact is detected. This concept is best explained at the hand of Figure xxx. The reference is split at the nominal impact time into an ante- and post impact reference. These references are then extended. Initially, the tracking error is based on the extended ante-impact reference, but this is switched to the post-impact reference once an impact is detected. Evidently, this can reduce the error peaking.

    Reference spreading can also handle simultaneous impacts. \cite{vansteenRobotControlSimultaneous2021} (explanation)

    By addressing the peaking error, reference spreading facilitates faster object manipulation, making it interesting to industry if its effectivity can be proven in practice. Reference spreading for object manipulation has already been validated in simulations \cite{vansteenRobotControlSimultaneous2021,zwartImpactAwareLearningDemonstration2019}. Experimental validations have been limited to interaction with a fixed environment, however \cite{rijnenReferenceSpreadingTracking2020,uitendaalTeachingRobotsInteraction2022}. The goal of this work is therefore to \textbf{provide a real-world implementation of reference spreading for practical object manipulation tasks.} To translate the results from simulation to reality, the following contributions are made:

    \textbf{1. Motion planning for impacts without object models}: Generating a reference with velocity jumps that is coherent with the system’s dynamics is challenging. 
    One approach maps the ante-impact velocity to the post-impact velocity based on conservation of momentum [ref for impact map]. This requires a model of the environment, which is feasible in simulations with simplified dynamics, but challenging in reality.
    Impact-driven velocity jumps could instead be inferred experimentally. In previous studies \cite{aouajPredictingPostImpactVelocity2021}, the control gains are reduced to zero upon detection of the impact while inferring an impact map, so that the velocity jump would not result in excessive motor torques.
    A different model-free motion planning strategy is proposed, which not only produces velocity-reference jumps that are coherent with the system dynamics, but also leverages human intuition to generate fluid motions before and after the impact. This is achieved by introducing a human in the loop by means of teleoperation. %(This strategy introduces a human in the loop by means of teleoperation; the operator performs a demonstration, after which a reference can be extracted. During the demonstration, the control gains are relatively low. This mitigates the torque jumps at the time of impact, meaning that the controller does not need to be turned off. The teleoperator instinctively accounts for the low control gains and can perform precise motion tasks despite poor tracking of the controller.)

    \textbf{2. Impact detection}: The reference spreading scheme should switch from ante- to post-impact references at the appropriate time. This requires an impact detection algorithm. Approaches in literature look either at position data \cite{rijnenMotionSignalsVelocity2018} or external force estimations \cite{uitendaalTeachingRobotsInteraction2022,properAimAwareCollisionMonitoring2021,properValidationNumericalSimultaneous2022} for signs that could be caused by impacts. We show that these signs are necessary, but not sufficient conditions for an impact -- only looking at position or contact force can result in false positives. To limit false detection of impacts, a novel impact detector that looks at both force and position data is described.

    \textbf{3. custom end effector, impedance control without inertia shaping with wrench saturation through stiffness optimization, contact task controller. Can these aspects be considered contributions?}
    %words: warehouse, material handling, packaging, transport

% Section
    \section{Controller}
    $$\ddot{p}_t = \ddot{p}_d + \Lambda^{-1}F_{imp}$$
    With 
    $$F_{imp} = D (\dot{p}_d-\dot{p}_t) + K((p_d+K^{-1}F_{ref})-p_t) $$

@@

% Section
    \section{MATH}

@@

% Section
    \section{USING THE TEMPLATE}

@@

% Conclusion
    \section{CONCLUSIONS}

@@

% Appendix
    \section*{APPENDIX}

@@

% References

@@

    % \addcontentsline{toc}{chapter}{Bibliography}
    % \printbibliography[title=References]
    \printbibliography

    % \begin{thebibliography}{99}

    % \bibitem{c1} G. O. Young, ``Synthetic structure of industrial plastics (Book style with paper title and editor),''  in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15--64.
    % \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123--135.
    % \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
    % \bibitem{c4} B. Smith, ``An approach to graphs of linear forms (Unpublished work style),'' unpublished.
    % \bibitem{c5} E. H. Miller, ``A note on reflector arrays (Periodical styleÑAccepted for publication),'' IEEE Trans. Antennas Propagat., to be publised.
    % \bibitem{c6} J. Wang, ``Fundamentals of erbium-doped fiber amplifiers arrays (Periodical styleÑSubmitted for publication),'' IEEE J. Quantum Electron., submitted for publication.
    % \bibitem{c7} C. J. Kaufman, Rocky Mountain Research Lab., Boulder, CO, private communication, May 1995.
    % \bibitem{c8} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interfaces(Translation Journals style),'' IEEE Transl. J. Magn.Jpn., vol. 2, Aug. 1987, pp. 740--741 [Dig. 9th Annu. Conf. Magnetics Japan, 1982, p. 301].
    % \bibitem{c9} M. Young, The Techincal Writers Handbook.  Mill Valley, CA: University Science, 1989.
    % \bibitem{c10} J. U. Duncombe, ``Infrared navigationÑPart I: An assessment of feasibility (Periodical style),'' IEEE Trans. Electron Devices, vol. ED-11, pp. 34--39, Jan. 1959.
    % \bibitem{c11} S. Chen, B. Mulgrew, and P. M. Grant, ``A clustering technique for digital communications channel equalization using radial basis function networks,'' IEEE Trans. Neural Networks, vol. 4, pp. 570--578, July 1993.
    % \bibitem{c12} R. W. Lucky, ``Automatic equalization for digital communication,'' Bell Syst. Tech. J., vol. 44, no. 4, pp. 547--588, Apr. 1965.
    % \bibitem{c13} S. P. Bingulac, ``On the compatibility of adaptive controllers (Published Conference Proceedings style),'' in Proc. 4th Annu. Allerton Conf. Circuits and Systems Theory, New York, 1994, pp. 8--16.
    % \bibitem{c14} G. R. Faulhaber, ``Design of service systems with priority reservation,'' in Conf. Rec. 1995 IEEE Int. Conf. Communications, pp. 3--8.
    % \bibitem{c15} W. D. Doyle, ``Magnetization reversal in films with biaxial anisotropy,'' in 1987 Proc. INTERMAG Conf., pp. 2.2-1--2.2-6.
    % \bibitem{c16} G. W. Juette and L. E. Zeffanella, ``Radio noise currents n short sections on bundle conductors (Presented Conference Paper style),'' presented at the IEEE Summer power Meeting, Dallas, TX, June 22--27, 1990, Paper 90 SM 690-0 PWRS.
    % \bibitem{c17} J. G. Kreifeldt, ``An analysis of surface-detected EMG as an amplitude-modulated noise,'' presented at the 1989 Int. Conf. Medicine and Biological Engineering, Chicago, IL.
    % \bibitem{c18} J. Williams, ``Narrow-band analyzer (Thesis or Dissertation style),'' Ph.D. dissertation, Dept. Elect. Eng., Harvard Univ., Cambridge, MA, 1993. 
    % \bibitem{c19} N. Kawasaki, ``Parametric study of thermal and chemical nonequilibrium nozzle flow,'' M.S. thesis, Dept. Electron. Eng., Osaka Univ., Osaka, Japan, 1993.
    % \bibitem{c20} J. P. Wilkinson, ``Nonlinear resonant circuit devices (Patent style),'' U.S. Patent 3 624 12, July 16, 1990.

    % \end{thebibliography}

### 2022-11-04 Progress_11.tex
Refs for paper + progress 11

% Summary 
  \section*{Progress meeting 10 | 24 October, 2022}

  \section*{1. Progress}
  \begin{itemize}

@@

@@

  Furthermore I added a feature where the VR device vibrates to indicate how much force is detected at the end effector. Personally I had difficulty with correlating the vibration with a force when teleoperating, and it also appeared that the vibrations were affecting the velocity reference extracted from the VR device. Overall I prefer teleoperation without the vibration.

  \end{itemize}

@@

  \begin{itemize}
      \item The controller that I have currently implemented does not benefit from reference spreading, and without reference spreading it cannot be considered impact aware. I see two possibilities here: add jumps to the velocity reference obtained from the VR device, or change damping behaviour briefly after impact. Do you perhaps have any suggestions?
      \item Alessandro previously proposed that I should write a paper+appendix rather than a report. Is this decision final? And are there any guidelines you recommend for writing such a paper?
  \end{itemize}

@@

  \begin{itemize}
      \item Make the controller impact-aware. Possible approaches are: adding jumps to the reference so that RS becomes useful, or briefly change damping behaviour after impact.
      \item Document custom end effector and impact detection comparison for final thesis.
      \item I realised that I do not yet fit ProMPs to data from multiple demonstrations. Fitting these ProMPs would reduce the noise in the velocity reference, and also filter out movements that are not required in fulfilling the task.
      \item (low priority/not absolutely required: look into using the force sensor for better impedance control in free motion as described in)
  \end{itemize}

  \section*{4. Long-term planning}
  Shown below is the current long-term planning for the project phase.  I believe that impact detection is finally finished. The impact-aware controller still requires a lot of effort, so I have reserved two weeks from the buffer to work on that. While reference processing and teleoperation are functional, there is still space for improvement, though the priority is on getting the entire impact-aware controller operating first.

>>>>

% Summary 
  \section*{Progress meeting 11 | 4 November, 2022}

  \section*{1. Progress}
  Parts in red have been added since the previous progress report.
  \begin{itemize}

@@

   \textcolor{red}{Evaluating reference spreading is one of the key goals of my project, and to do that, the velocity reference must contain jumps. Therefore I implemented a controller that tracks the position/velocity of the robot arm during demonstration (so not the VR device). I used feed forward to control the contact force, which worked as desired in simulation. Experiments on the real system were less succesful, presumably due to friction, though this still needs more investigation. Nevertheless, I will discuss with Jari if feedforward really is the way to go.  }

@@

   \textcolor{red}{Alessandro suggest that I move the point on the robot that I try to control to be in line with the wrist joints of the robot. This allowed for better tracking of the angular DoF's without exceeding safety constraints. Furthermore, I removed the velocity limit that I previously applied to the VR device signals, and am now limiting the impedance wrench instead. I can now reach end effector velocities of 1.5 m/s and 1.5 rad/s.}

  Furthermore I added a feature where the VR device vibrates to indicate how much force is detected at the end effector. Personally I had difficulty with correlating the vibration with a force when teleoperating, and it also appeared that the vibrations were affecting the velocity reference extracted from the VR device. Overall I prefer teleoperation without the vibration.
    \color{red}
  \item  \textbf{Misc:}  I made a pallet of 40x60 cm for making nicer videos/demos. Furthermore I started on the introduction of my final report. I also looked into some questions Alesandro had about Sven's work:

  \textbf{Did Sven use the VR device or a hardcoded reference for the demonstrations?}
  Sven ended up using hardcoded references (with small randomly generated variances) to ensure that the impact occurred under relatively similar conditions

\textbf{Did Sven use the same impedance controller used during demonstration and replays?}
  Yes, the controller used during demonstration is the same as the ante-impact phase controller. The stiffnesses also remain unchanged (400 N/m in x and y direction, 1080 N/m in z direction, and 50 Nm/rad in orientation. For comparison, I am using 800 N/m and 50 Nm/rad)

\textbf{Did Sven apply reference spreading to the VR device position or to measured robot positions/velocities/forces during the demonstration?}
  Reference spreading was applied to robot measurements during the demonstration. 
\color{black}
  \end{itemize}

@@

  \begin{itemize}
      \item During the last meeting, we did not have the time to talk about impact discussion, so let's go over that today.
      \item Previously, it was proposed that I should write a paper+appendix rather than a report. Is this decision final? And are there any guidelines you recommend for writing such a paper?
      \item For the contact phase controller, I want to discuss with Jari, but if time allows it we can already talk about it during this meeting.
  \end{itemize}

@@

  \begin{itemize}
      \item Implement a contact-phase controller that does not need a complete model of the environment (for example, I do not know the location of the box).
      \item Compare the performance of the controller with and without reference spreading
      \item Reporting
  \end{itemize}

  \section*{4. Long-term planning}
  Shown below is the current long-term planning for the project phase.  I believe that impact detection is finally finished. I have added another two weeks to the RS controller, but further extensions would start to interfere with writing my report.
